Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-10-14 Final_Manuscript.tex
cleaned up a bunch

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Fredrickson and Roberts (1997)'s Objectification Theory, suggests that,
in addition to being steeped in a culture that objectifies women, women
are objectified in actual interpersonal encounters. The negative effects
of this interpersonal objectification for women have been theorized to
be the strongest under the \enquote{male gaze,} that is, when it is a
percieved or actual man doing the objectifying (Calogero, 2004; Gay \&
Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
consequences when a woman objectifies another woman in an interaction?
Psychological researchers studying the sexual objectification of women
have in recent years explored the interpersonal process of the
objectification, finding evidence for \emph{self}-objectification in the
target as a proximal consequence of being objectified (Garcia et al.,
2016; Riemer, Sáez, Brock, \& Gervais, 2020; Strelan \& Pagoudis, 2018).
In a recent review, Gervais et al. (2020) organized the extant
literature on interpersonal self-objectification and proposed a
theoretical model called the Social Interaction Model of Objectification
(SIMO). The SIMO is useful for studying mixed-gender interactions, but
can it be extended to interactions among women? Although there is
evidence that women objectify other women (Loughnan et al., 2015a; Puvia
\& Vaes, 2013), studies investigating the process of interpersonal
objectification in interactions between women is scarce.

@@

Self-objectification is a psychological process that translates the
experiences of interpersonal objectification (Gervais et al., 2020;
Loughnan et al., 2015a) into negative mental health outcomes (e.g.,
interaction inauthenticity, anxiety, lower self-esteem, and poor
cognitive performance; Calogero, Tantleff-Dunn, \& Thompson, 2011;
Moradi \& Huang, 2008). Calogero et al. (2011) proposes that
self-objectification can be conceptualized as a learned trait, or
\emph{trait} self-objectification (TSO), whereby one abopts a habitual
third-person perspective on one's own appearance. Furthermore,
self-objectification can also be elicited momentarily, for example, when
viewing sexualized images in movies and magazines (Morry \& Staska,
2001), when trying on sexualizing clothing (Barbara L Fredrickson,
Roberts, Noll, Quinn, \& Twenge, 1998), or during video chat when you
believe your interaction partner can only see your body (not face;
Saguy, Quinn, F Dovidio, \& Pratto, 2010). This momentary
self-objectification is referred to as \emph{state} self-objectification
(SSO; Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
Huang, 2008) and is characterized by feeling like a body rather than a
full self within a particular moment, instance, or context.

There is evidence that being objectified by another person during an
interaction elicits SSO. For example, Loughnan, Baldissarri, Spaccatini,
and Elder (2017) found that for women, imagining a time when they were
objectified by another person caused reductions in human traits
attributed to the self, and notably, the gender of the person doing the
objectification was not a moderating factor. In addition, in a
mixed-gender dyadic study of actual interactions, Garcia et al. (2016)
found that men's reported objectification of their female interaction
partner was associated with increased self-objectification (as reported
by their female partner). Further, this negative effect of the men's
objectification on women's SSO was strongest for women higher in TSO.
The current study uses this same dyadic paradigm to study same-gender,
woman-woman interacting pairs.

@@

Past research investigating women objectifying other women has focused
on the psychological conditions that led women to objectify women.
Harsey and Zurbriggen (2020) found that (trait) self-objectification was
related to the objectification of women to a similar degree for male and
female participants. Along the same lines, Strelan and Hargreaves (2005)
found that the more women self-objectify, the more they objectify other
women. Could the process work in the other direction as well, that is,
could objectification by a woman produce (state) self-objectification,
in a similar manner to objectification by a man? Hill and Fischer (2008)
assessed women's experiences of objectification from men independently
from women's experiences of objectification from other women. They found
that women may be socialized not only to see themselves as objects, but
perhaps to see other women as objects as well. This process, however,
was not comfirmed to occur during an actual interpersonal interaction.
Thus, there is evidence that women do objectify other women, indeed,
Loughnan et al. (2015a) found that women objectify other women to a
greater extent than they objectify men. Women have also been found to
objectify (dehumanized) sexualized targets presented as images (Puvia \&
Vaes, 2013), but very little is known about interpersonal sexual
objectification among women and what the effects of this objectification
might be. Past studies have foud that objectification has more adverse
consequences for women than men (Gervais et al., 2011; Moradi \& Huang,
2008; Saguy et al., 2010), however, we do not know much about the effect
of the gender of the \emph{objectifyer} on potential detrimental
outcomes.

@@

Studies have shown that within social encounters women are gazed at more
than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
within interpersonal interactions (Argyle \& Williams, 1969;
Miles-McLean et al., 2015), and are likely to internalize the
objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
1979). As mentiond above, interpersonal objectification has been found
to have negative consequences for women. Gervais et al. (2011) found
that an objectifying gaze by a male interaction partner (confederate)
was associated with lower math performance for women than being
objectified by a female interaction partner. Perhaps the most adverse
negative consequence of interpersonal objectificaiton is that being
objectified socializes girls and women to routinely treat themselves as
objects to be looked at and evaluated (Bartky, 1990; Berger, Cohen, \&
Zelditch Jr, 1972; Barbara L Fredrickson et al., 1998). Gervais et al.
(2020) recently reviewed the research on interpersonal objectification
and organized our current theoretical understanding of this process in
the Social Interaction Model of Objectification (SIMO). What is clear
from Gervais et al. (2020)'s review is that we know little about
women-on-women interpersonal objectification. Could there also be
negative consequences for women after being objectified by a woman?

Past research has found that the experience of state
self-objectification in mixed-gender contexts (stranger and romantic;
Strelan and Pagoudis (2018); Meltzer (2020)) has negative consequences
for women, but what about in the context of interactions with other
women? Is the self-objectification experienced in mixed-gender
interactions associated with the same negative process as that
experienced in same-gender interactions? The ample research
demonstrating that the male gaze has a particularly detrimental effect
for women would suggest no (Calogero, 2004; Gay \& Castano, 2010;
Gervais et al., 2011; Saguy et al., 2010; Yilmaz \& Bozo, 2019), but,
there is evidence that women do objectify other women (Harsey \&
Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and it
would be helpful to understand the consequencs of this \emph{intra}group
objectification for women. When women objectify other women, does it
lead to self-objectification in the same way men's objectification of
women does (Garcia et al., 2016)? If so, does the self-objectification
experienced in these same-gender interactions have the same negative
consequences for authenticity in that interaction?

There is some evidence that reduced authenticity is a consequence of
self-objectification (Garcia et al., 2016; Terán, Jiao, \& Aubrey,
2020). A recent study has investigated the effect of
self-objectification on the reduction of relationship building skills in
general (including same-sex friendships) (Terán et al., 2020). This link
has also been found in research on stigmatized-stigmatizer interactions
(M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003; Shelton,
Richeson, \& Salvatore, 2005), and we might view the experience of being
objectified in an interaction as a potential identity threat,
stigmatizing, situation (Miles-McLean et al., 2015; Nadal \& Haynes,
2012). Further, empirical evidence reveals that objectification
manifests through inauthenticity in romantic relationships (Brunell et
al., 2010), an intergroup context at least in heterosexual
relationships. Evidence for otehr adverse consquences of interpersonal
objectification include reductions in career aspirations (Garcia et al.,
2016) and a decrease in concentration and impairment in female cognitive
performance (Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir,
\& Kallen, 2011). These are also negative conseqences found for women
under steroetype threat (Davies, Spencer, \& Steele, 2005). When a woman
is objectified by a man, and subsequently experiences
self-objectification, the intergroup nature of this encounter might
trigger threat. Thus, perhaps there are fewer negative consequences when
a woman is objectified by another woman. That is, the intergroup threat
literature might predict that woman-woman interpersonal objectification
processes diverge from mixed-gender interpersonal objectification
processes precisely because they are not intergroup interactions (at
least with respect to gender identity).

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:corrtable}Correlations and Descriptive Statistics among Study Variables}
\begin{tabular}{llllllllll}
\toprule
 & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{NA}\\
\midrule
1. Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  &  &  & \\
2. Actor's objectification of partner & -1.58 & 1.21 & .20 &  &  &  &  &  & \\
3. Partner's objectification of the actor & -1.58 & 1.21 & .09 & .14 &  &  &  &  & \\
4. Actor's state self-objectification & 1.92 & 1.13 & .13 & -.09 & .30* &  &  &  & \\
5. Actor's authenticity of interaction & 5.23 & 1.02 & -.02 & -.07 & .03 & -.10 &  &  & \\
6. Actor's future relationship agency & 4.69 & 0.96 & .04 & .09 & -.10 & -.09 & .23+ &  & \\
7. Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .06 & .02 & .11 & .07 & \\
8. Actor's career aspirations & 3.88 & 0.61 & .05 & -.14 & -.08 & .01 & .33** & .26* & -.07\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

@@

Trait self-objectification (TSO) was assessed using the
Self-Objectification Questionnaire (Barbara L Fredrickson et al., 1998;
M. Noll \& L. Fredrickson, 1998), which evaluates the extent to which
individuals view their bodies in observable versus non-observable ways.
The questionnaire asked participants to rank order both appearance and
functional aspects of their bodies, from 1 (least important) to 10 (most
important), with respect to physical self-concepts. Of the ten body
attributes, five of the items were appearance-based (weight, sex appeal,
physical attractiveness, firm/sculpted muscles and body measurements),
and five of the items were competence-based (strength, physical
coordination, energy level, health and physical fitness). Difference
scores were computed by subtracting the sum of the 5 functional
aspects/competence attributes (e.g., health, strength) from the sum of
the 5 physical self-concepts/appearance attributes (e.g., physical
attractiveness, weight), and all measures were multiplied by -1 so that
positive scores indicated greater TSO.

@@

In addition to partner other-objectification, this model also included
one's own objectification of their partner (actor
other-objectification), actor trait self-objectification (TSO), and the
interaction of partner other-objectification and TSO. One's own other
objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE} =
0.12, \emph{p} = .210. Further, inconsistent with past findings however,
there was no statistically significant interaction of partner's other
objectification and the person's trait self-objectification on SSO,
\emph{b} = 0.03, \emph{SE} = 0.27, \emph{p} = .910. There was also no
significant main effect of trait self-objectification on SSO \emph{b} =
0.07, \emph{SE} = 0.05, \emph{p} = .183. The \(R^2\) of this model was
0.03. As a test of the potential alternative models discussed above, we
ran a MLM with other-objectification predicted by actor TSO but there
was no statistically significant relationship between these two
variables, \emph{b} = 0.09, \emph{SE} = 0.06, \emph{p} = .133.

@@

The current study tested whether the model of interpersonal
objectification and state self-objectification (SSO) used in Garcia et
al. (2016) replicates in a same-gender dyadic sample of women. Although
past research has found that women do objectify other women (Harsey \&
Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), this is
the first study to test if \emph{interpersonal} other-objectification by
women is related to state self-objectification in their woman-identified
interaction partners. As hypothesized, the current study did find a
significant relationship between a woman's interaction partner's report
of having objectified her and her own post-interaction feelings of
self-objectification. That is, there was a significant partner effect of
other-objectification on SSO. This effect extends the equivalent
relationship found in mixed-gender interactions to the context of
same-gender interactions between women. Thus, evidence suggests that it
is not only the male gaze, and male other-objectification that is
related to women's state self-objectification, but being objectified by
another woman is also related to women's SSO, at least in the context of
a scenario where they know they are being evaluated as a potential
dating partner.

As is the case in all correlational studies, we cannot be sure about the
causal direction. The model used by the current study asserts that being
objectified by a woman causes women to self-objectify, but it could be
that women's SSO causes them to be objectified by their interaction
partner. This latter interpretation is theoretically interesting given
that, in both the Garcia et al. (2016) study and in the current study,
it is \emph{women's} state self-objectification that relates to being
objectified by one's partner. Objectification Theory (Fredrickson \&
Roberts, 1997), as well as some past experimental studies (Saguy et al.,
2010) suggest that at least one direction of the causal flow is from
other-objectification to SSO. Other studies, especailly those
investigating explicitly women objectifying other women (Puvia \& Vaes,
2013), have relately found evidence that women's \emph{trait}
self-objectification causes women to objectify (dehumanize) other women
and this link is mediated by \emph{state} self-objectification. It could
follow that we tend to objectify other women who objectify us and
through a process of TSO causes SSO which in turn causes objectifation
of one's partner, which in turn causes one's partner to objectify us.
The current study does not provide any evidence of this alternative
model, however---TSO was not significantly correlated with SSO and
actor's objectification was not correlated with partner's
objectification.

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
            pdfkeywords={Interpersonal sexual objectification, self-objectifiation, authenticity,
actual interactions, psychology of women, dyadic data analysis},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
\keywords{Interpersonal sexual objectification, self-objectifiation, authenticity, actual interactions, psychology of women, dyadic data analysis}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Fredrickson and Roberts (1997)'s Objectification Theory, suggests that,
in addition to being steeped in a culture that objectifies women, women
are objectified in actual interpersonal encounters. The negative effects
of this interpersonal objectification for women have been theorized to
be the strongest under the \enquote{male gaze,} that is, when it is a
percieved or actual man doing the objectifying (Calogero, 2004; Gay \&
Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
consequences when a woman objectifies another woman in an interaction?
Psychological researchers studying the sexual objectification of women
have in recent years explored the interpersonal process of the
objectification, finding evidence for \emph{self}-objectification in the
target as a proximal consequence of being objectified (Garcia et al.,
2016; Riemer, Sáez, Brock, \& Gervais, 2020; Strelan \& Pagoudis, 2018).
In a recent review, Gervais et al. (2020) organized the extant
literature on interpersonal self-objectification and proposed a
theoretical model called the Social Interaction Model of Objectification
(SIMO). The SIMO is useful for studying mixed-gender interactions, but
can it be extended to interactions among women? Although there is
evidence that women can objectify other women (Gervais, Holland, \&
Dodd, 2013; Loughnan et al., 2015; Puvia \& Vaes, 2013), studies
investigating the process of interpersonal objectification in
interactions between women is scarce.

@@

Self-objectification is a psychological process that translates the
experiences of interpersonal objectification (Gervais et al., 2020;
Loughnan, Baldissarri, Spaccatini, \& Elder, 2017) into negative mental
health outcomes (e.g., interaction inauthenticity, anxiety, lower
self-esteem, and poor cognitive performance; Calogero, Tantleff-Dunn, \&
Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
that self-objectification can be conceptualized as a learned trait, or
\emph{trait} self-objectification (TSO), whereby one abopts a habitual
third-person perspective on one's own appearance. Furthermore,
self-objectification can also be elicited momentarily, for example, when
viewing sexualized images in movies and magazines (Morry \& Staska,
2001), when trying on sexualizing clothing (B. L. Fredrickson, Roberts,
Noll, Quinn, \& Twenge, 1998), or during video chat when you believe
your interaction partner can only see your body (not face; Saguy, Quinn,
F Dovidio, \& Pratto, 2010). This momentary self-objectification is
referred to as \emph{state} self-objectification (SSO; Calogero et al.,
2011; Moradi \& Huang, 2008) and is characterized by feeling like a body
rather than a full self within a particular moment, instance, or
context.

There is evidence that being objectified by another person during an
interaction elicits SSO. For example, Loughnan et al. (2017) found that
for women, imagining a time when they were objectified by another person
caused reductions in human traits attributed to the self, and notably,
the gender of the person doing the objectification was not a moderating
factor. In addition, in a mixed-gender dyadic study of actual
interactions, Garcia et al. (2016) found that men's reported
objectification of their female interaction partner was associated with
increased self-objectification (as reported by their female partner).
Further, this negative effect of the men's objectification on women's
SSO was strongest for women higher in TSO. The current study uses this
same dyadic paradigm to study same-gender, woman-woman interacting
pairs.

@@

Past research investigating women objectifying other women has focused
on the psychological conditions that led women to objectify women.
Harsey and Zurbriggen (2020) found that (trait) self-objectification was
related to the objectification of women to a similar degree for male and
female participants. Along the same lines, Strelan and Hargreaves (2005)
found that the more women self-objectify, the more they objectify other
women. Could the process work in the other direction as well, that is,
could objectification by a woman produce (state) self-objectification,
in a similar manner to objectification by a man? Hill and Fischer (2008)
assessed women's experiences of objectification from men independently
from women's experiences of objectification from other women. They found
that women may be socialized not only to see themselves as objects, but
perhaps to see other women as objects as well. This process, however,
was not comfirmed to occur during an actual interpersonal interaction.
Thus, there is evidence that women do objectify other women, indeed,
Loughnan et al. (2017) found that women objectify other women to a
greater extent than they objectify men. Women have also been found to
objectify (dehumanized) sexualized targets presented as images (Puvia \&
Vaes, 2013), but very little is known about interpersonal sexual
objectification among women and what the effects of this objectification
might be. Past studies have foud that objectification has more adverse
consequences for women than men (Gervais et al., 2011; Moradi \& Huang,
2008; Saguy et al., 2010), however, we do not know much about the effect
of the gender of the \emph{objectifyer} on potential detrimental
outcomes.

@@

Studies have shown that within social encounters women are gazed at more
than men (Henley, 1977), often times feel \enquote{looked at} within
interpersonal interactions (Argyle \& Williams, 1969), and are likely to
internalize the objectifying gaze on their physical self (Puvia \& Vaes,
2013; Young, 1979). As mentiond above, interpersonal objectification has
been found to have negative consequences for women. Gervais et al.
(2011) found that an objectifying gaze by a male interaction partner
(confederate) was associated with lower math performance for women than
being objectified by a female interaction partner. Perhaps the most
adverse negative consequence of interpersonal objectificaiton is that
being objectified socializes girls and women to routinely treat
themselves as objects to be looked at and evaluated (Bartky, 1990; B. L.
Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
research on interpersonal objectification and organized our current
theoretical understanding of this process in the Social Interaction
Model of Objectification (SIMO). What is clear from Gervais et al.
(2020)'s review is that we know little about women-on-women
interpersonal objectification. Could there also be negative consequences
for women after being objectified by a woman?

Past research has found that the experience of state
self-objectification in mixed-gender contexts (stranger and romantic;
Strelan and Pagoudis (2018); Meltzer (2020)) has negative consequences
for women, but what about in the context of interactions with other
women? Is the self-objectification experienced in mixed-gender
interactions associated with the same negative process as that
experienced in same-gender interactions? The ample research
demonstrating that the male gaze has a particularly detrimental effect
for women would suggest no (Calogero, 2004; Gay \& Castano, 2010;
Gervais et al., 2011; Saguy et al., 2010; Yilmaz \& Bozo, 2019), but,
there is evidence that women do objectify other women (Harsey \&
Zurbriggen, 2020; Loughnan et al., 2015; Puvia \& Vaes, 2013) and it
would be helpful to understand the consequencs of this \emph{intra}group
objectification for women. When women objectify other women, does it
lead to self-objectification in the same way men's objectification of
women does (Garcia et al., 2016)? If so, does the self-objectification
experienced in these same-gender interactions have the same negative
consequences for authenticity in that interaction?

There is some evidence that reduced authenticity is a consequence of
self-objectification (Garcia et al., 2016; Terán, Jiao, \& Aubrey,
2020). A recent study has investigated the effect of
self-objectification on the reduction of relationship building skills in
general (including same-sex friendships) (Terán et al., 2020). This link
has also been found in research on stigmatized-stigmatizer interactions
(M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003; Shelton,
Richeson, \& Salvatore, 2005), and we might view the experience of being
objectified in an interaction as a potential identity threat,
stigmatizing, situation (Gervais et al., 2020; Nadal \& Haynes, 2012).
Further, empirical evidence reveals that healthy relationship
functioning manifests through authenticity in romantic relationships
(Brunell et al., 2010), an intergroup context at least in heterosexual
relationships. Evidence for otehr adverse consquences of interpersonal
objectification include reductions in career aspirations (Garcia et al.,
2016) and a decrease in concentration and impairment in female cognitive
performance (Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir,
\& Kallen, 2011). These are also negative conseqences found for women
under steroetype threat (Davies, Spencer, \& Steele, 2005). When a woman
is objectified by a man, and subsequently experiences
self-objectification, the intergroup nature and power differential of
this encounter might trigger threat. Thus, perhaps there are fewer
negative consequences when a woman is objectified by another woman. That
is, the intergroup threat literature might predict that woman-woman
interpersonal objectification processes diverge from mixed-gender
interpersonal objectification processes precisely because they are not
intergroup interactions (at least with respect to gender identity).

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:corrtable}Correlations and Descriptive Statistics among Study Variables}
\begin{tabular}{llllllllll}
\toprule
 & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{7.}\\
\midrule
1. Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  &  &  & \\
2. Actor's objectification of partner & -1.58 & 1.21 & .20 &  &  &  &  &  & \\
3. Partner's objectification of the actor & -1.58 & 1.21 & .09 & .14 &  &  &  &  & \\
4. Actor's state self-objectification & 1.92 & 1.13 & .13 & -.09 & .30* &  &  &  & \\
5. Actor's authenticity of interaction & 5.23 & 1.02 & -.02 & -.07 & .03 & -.10 &  &  & \\
6. Actor's future relationship agency & 4.69 & 0.96 & .04 & .09 & -.10 & -.09 & .23+ &  & \\
7. Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .06 & .02 & .11 & .07 & \\
8. Actor's career aspirations & 3.88 & 0.61 & .05 & -.14 & -.08 & .01 & .33** & .26* & -.07\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

@@

Trait self-objectification (TSO) was assessed using the
Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; S.
Noll \& Fredrickson, 1998), which evaluates the extent to which
individuals view their bodies in observable versus non-observable ways.
The questionnaire asked participants to rank order both appearance and
functional aspects of their bodies, from 1 (least important) to 10 (most
important), with respect to physical self-concepts. Of the ten body
attributes, five of the items were appearance-based (weight, sex appeal,
physical attractiveness, firm/sculpted muscles and body measurements),
and five of the items were competence-based (strength, physical
coordination, energy level, health and physical fitness). Difference
scores were computed by subtracting the sum of the 5 functional
aspects/competence attributes (e.g., health, strength) from the sum of
the 5 physical self-concepts/appearance attributes (e.g., physical
attractiveness, weight), and all measures were multiplied by -1 so that
positive scores indicated greater TSO.

@@

In addition to partner other-objectification, this model also included
one's own objectification of their partner (actor
other-objectification), actor trait self-objectification (TSO), and the
interaction of partner other-objectification and TSO. One's own other
objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE} =
0.12, \emph{p} = .210. Further, inconsistent with past findings however,
there was no statistically significant interaction of partner's other
objectification and the person's trait self-objectification on SSO,
\emph{b} = 0.03, \emph{SE} = 0.27, \emph{p} = .910. There was also no
significant main effect of trait self-objectification on SSO \emph{b} =
0.07, \emph{SE} = 0.05, \emph{p} = .183. The \(R^2\) of this model was
0.03.

As a test of the potential alternative models discussed above---if
trait-self-objectification is related to objectifying one's partner to a
greater degree---we ran a MLM with other-objectification predicted by
actor TSO. There was no statistically significant relationship between
these two variables, \emph{b} = 0.09, \emph{SE} = 0.06, \emph{p} = .133.
We also ran a model with both TSO and SSO predicting
other-objectification, given past theorizing that state
self-objectification might mediate the relationship between TSO and
objectification of fellow women, but there was no effect of SSO on
other-objectification in this model, \emph{b} = -0.17, \emph{SE} = 0.13,
\emph{p} = .199.

@@

The current study tested whether the model of interpersonal
objectification and state self-objectification (SSO) used in Garcia et
al. (2016) replicates in a sample of women engaging in actual dyadic
interactions with each other. Although past research has found that
women do objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et
al., 2015; Puvia \& Vaes, 2013), this is the first study to test if
\emph{interpersonal} other-objectification by women during actual
interactions is related to state self-objectification in their
woman-identified interaction partners. As hypothesized, the current
study did find a significant relationship between a woman's interaction
partner's report of having objectified her and her own post-interaction
feelings of self-objectification. That is, there was a significant
partner effect of other-objectification on SSO. This effect extends the
equivalent relationship found in mixed-gender interactions to the
context of same-gender interactions between women. Thus, evidence
suggests that it is not only the real or imagined male gaze that is
related to women's state self-objectification, but there is now also
evidence that being objectified by another woman could be related to
women's SSO, at least in the context of a scenario where they know they
are being evaluated as a potential dating partner.

As is the case in all correlational studies, we cannot be sure about the
causal direction between other-objectification and SSO. The linear model
used by the current study implies that being objectified by a woman
leads women to self-objectify, but it could be that women's SSO causes
them to be objectified by their interaction partner. This latter
interpretation is possible given the empiricle evidence that it is
\emph{women's} state self-objectification that relates to being
objectified by one's partner---men partners (Garcia et al., 2016) and
now women partners. Objectification Theory (Fredrickson \& Roberts,
1997), as well as some past experimental studies (for example, Saguy et
al., 2010), suggest that the causal flow is from other-objectification
to SSO. Other studies, especailly those investigating explicitly women
objectifying other women (Puvia \& Vaes, 2013), have relately found
evidence that women's \emph{trait} self-objectification is related to
women objectifying (dehumanizing) other women and this link is mediated
by \emph{state} self-objectification. The process of interpersonal
objectification among women could also contain a feedback loop. That is,
perhaps we tend to objectify other women who objectify us and through a
process of TSO causing SSO which in turn causes objectifation of one's
partner, which in turn causes one's partner to objectify us. However,
the current study does not provide any evidence of the TSO to
other-objectifixation link---TSO was not significantly correlated with
SSO and, further, actor's other-objectification was not correlated with
partner's other-objectification.

Where the results of the current study diverge most notably from the
results of studies testing interpersonal objectification among
mixed-gender dyads is the lack of evidence for relationships between SSO
and interaction inauthenticity.\footnote{In addition, we found no
  evidence of \emph{direct} or \emph{indirect} relationships between SSO
  and cognitive functioning, relationship agency, and career
  aspirations. Nor was there evidence of \emph{direct} or
  \emph{indirect} relationships between other-objectification and any of
  these outcomes.} This is somewhat suprising given the extant evidence
linking SSO and cognitive functioning (B. L. Fredrickson et al., 1998;
and see Moradi \& Huang, 2008 for a review; Quinn, Chaudoir, \& Kallen,
2011) and the research on interpersonal other-ojectification and
cognitive functioning (Garcia et al., 2016; Gervais et al., 2011; Logel
et al., 2009). This lack of evidence could potentially signal diverging
processes between women's experiences with interpersonal objectification
from men and interpersonal objectification from women. There is quite a
bit of evidence suggesting that the male gaze is particularly
detrimental (Calogero, 2004; Fredrickson \& Roberts, 1997; Gervais et
al., 2011), and perhaps the self-objectification experienced within an
interaction with a women is qualitatively different, and perhaps not as
harmful, as the state self-objectification experienced within an
interaction with a man. However, as a strong note of caution, it is best
not to interpret a null result as evidence of no relationship and more
research on interpersonal objectification among women is needed.

The lack of evidence for a relationship between SSO and interaction
authenticity is surprising and again, should not be interpreted as
evidence of no relationship. It should be noted that the estimate of
this relationship was small (close to zero), but in the negative
direction. If it is the case that there is a smaller (i.e., weaker) or
zero connection between women's feelings of SSO and inauthenticity in
interactions with other women than in interactions with men, models of
interpersonal objectification, like the SIMO (Gervais et al., 2020),
could be extended by including gender of the objectifyer/interaction
partner as a moderator. Inauthenticity could be added as a potential
moderated mediating factor to help understand the circumstances that
require other-objectification and SSO to have negative consequences for
women. Perhaps one important difference is the lack of a power
differential across gendered lines -- the patriarchy is present, but the
interafction partners are not a stigmatizer-stigmatized pair.
